### 2023-02-19 paper.tex
Added more offline concepts. Added new concepts section.

 \begin{itemize}
    \item Online Concepts
        \begin{itemize}
            \item Playback
            \item Master-Slave
            \item Teach-in
            \item CAD/graphical based
        \end{itemize}
    \item Offline Concepts
        \begin{itemize}
            \item CAD/graphical based
            \item text based
            \item task based
                \begin{itemize}
                    \item explicit
                    \item implicit
                \end{itemize}
            \item Simulation
        \end{itemize}
    \item Hybrid Concepts
 \end{itemize}

@@

\section{Offline Concepts}
    \subsection{CAD/graphical based}
    \subsection{text based}

@@

@@

    \subsection{task based}
        \subsubsection{explicit}
        \subsubsection{implicit}
    \subsection{CAD/graphical based}

@@

@@

\begin{thebibliography}{00}
    \bibitem{b1} Wolfgang Weber, Heiko Koch, ''Industrieroboter Methoden der Steuerung und Regelung'' Carl Hanser Verlag München, 5. Auflage, 2022

\end{thebibliography} 
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

@@

>>>>

old-fashioned concepts
widely used in the industry

 \begin{itemize}
    \item Online Concepts
        \begin{itemize}
            \item Playback
            \item Master-Slave
            \item Teach-in
            \item CAD/graphical based
        \end{itemize}
    \item Offline Concepts
        \begin{itemize}
            \item CAD/graphical based
            \item text based
            \item task based
            \item Simulation
        \end{itemize}
    \item Hybrid Concepts
 \end{itemize}

new or theoretical concepts
not widely used in the industry, published in scientific papers

\begin{itemize}
    \item Semantic Robot Programming
    %\item AI
    %\item AR
%\item VR
\end{itemize}

@@

\section{Offline Concepts}

    development doesn't take place on an active robot itsself but on a seperate system, indirect programming
    the program gets loaded onto the robot later on

     (b4 p 186)

    \subsection{CAD/graphical based}
    \subsection{text based}

        text based = explicit
        you tell how to move to accomplish a certain task

@@

        there are many programming languages to choose from developing using the textual concept
        based on the 2019 market share of todays biggest robot manufacturers the most commong languages used are KAREL, RAPID, KRL
        (s1)

@@

    \subsection{task based}

        task based = implicit
        you tell what task to do to achieve a certain goal
        more abstract than text based, adds a layer of abstraction to the programming workflow

        description of the tasks gets translated into lines of code by a task transformer (b1 p 116)

        uses sensor information to add dynamic to the program while running

        example task based programming enviroment:
        RoboGuide from FANUC defining by drag and drop
        Visual Components by flowchart
        Robotmaster

    \subsection{CAD/graphical based}

@@

    mixing of both offline and online concepts
    can be done by creating a general program offine and later  fine tune this programm with online concepts on the real robot
    or the other way around by first programming the robot online and then optimizing the program offline
    (b4 p 186)

\section{New Concepts} %?

    \subsection{Semantic Robot Programming}

        = programming by demonstrating

        in a paper ... the authors propose a new concept of programming robots by demonstrating the desired behavior to the robot by giving an initial state and a goal state for which the robot has to find the best way to get from the initial state to the goal state

        they use a new scene estimation method called DIGEST which splits the scene into a scene graph representing the scene structure of the initial state
        only requirement is the information about the number of objects present in the scene

        given now the structure of the initial state and the goal, a task planer to find the best way to get from the initial state to the goal state is used

        the task planer generates a series of actions to accomplish the task
        (p1 p 2)

    \subsection{AR}

        (p3)

    \subsection{VR}

        (p2)

@@

\nocite{*}

\bibliographystyle{unsrt}
\bibliography{quellen}

@@

%maybe add the statics cited in the text?
